Benchmarking Python Deep Learning Frameworks\\ for Language Modeling on GPUs

### 2016-12-14 paper/main.tex
update dynet footnote in 2.2; update theano install in 5.2.1

All of the frameworks we tested have Python APIs\footnote{DyNet was originally a C++ framework which now has a Python wrapper; currently its Python wrapper only supports Python 2. TensorFlow and Theano are primarily Python frameworks that support both Python 2 and 3.} that wrap C++ or optimized Python code (e.g., numpy).

@@

@@

>>>>

All of the frameworks we tested have Python APIs\footnote{DyNet was originally a C++ framework which now has a Python wrapper; currently its Python wrapper seems to only support Python 2. TensorFlow and Theano are primarily Python frameworks that support both Python 2 and 3.} that wrap C++ or optimized Python code (e.g., numpy).

@@

\paragraph{DyNet} We encountered some difficulties in installing DyNet. The library failed to build with the recommended development version of Eigen, so we had to revert to an earlier commit. We also had to use Python 2 for the Python interface, though the documentation says it supports Python 3.

\paragraph{TensorFlow}

\paragraph{Theano} Our experience with Theano installation was relatively straightforward: pip install of relevant modules and specification of the BLAS install location.

@@

\paragraph{TensorFlow} \textless TensorFlow stuff goes here \textgreater
